Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: 0926

    = e^{-\langle u_f(\cdot , t), \mu \rangle},

@@

where $(x,t) \mapsto u_f(x, t)$ is the unique locally bounded positive solution to the equation

@@

     u_f(x , t) + \Pi_x \Big[ \int_0^t\psi\big(u_f(\xi_s,t-s)\big)~ds\Big]

@@

    The existence of such superprocesses is well known, see \cite{EB} for instance.
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
    The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example.
    In fact,
\begin{equation}
    \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
%comment
    {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$. Because we want to emphsis that our superprocess is non-presistent.)}
%end comment

    Define the \emph{Fenyman-Kac semigroup} by
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    := \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.

@@

    %In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
    In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is easy to see that $\mathcal{P} \subset L^2(\varphi)$.
    %According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
\begin{equation}
\label{eq:semigroupineq}
    |T_tf(x)| 
    \leq e^{-\kappa(f)bt} R(x),
    \quad t\geq 0, x\in \mathbb R^d.
\end{equation}

@@

    Let $X$ be the super OU-process discussed in the previous subsections.
    Its branching mechanism $\psi$ can be extended in the following way: $\psi(z) := -\alpha z + z^{1+\beta}$ for $z\in \mathbb C_+$. 
    Then according to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
Write $\psi_0(z) = \psi(z) + \alpha z$ and $\psi'_0(z) = \psi'(z) + \alpha$.
%end new added
    %For any $f \in \mathcal{P}$, replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
%\begin{equation}\label{characteristic}
    %\mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
%\end{equation}
%where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
%\begin{equation}\label{charequation}
    %w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
%\end{equation}
    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $w_f(x,t,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$ the characteristic exponent of $\{X_t(f); \mathbb P_{\delta_x}\}$
    (For percise definition, see the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $- w_f(x,t,\theta)$ taks values in $\mathbb C_+$.
    Furthermore, we know from Proposition \ref{sec: definition of characteristic exponent} that
%delete
%\begin{equation}\label{characteristic}
    %\mathbb{P}_{\mu}[e^{i\theta X_t(f)}]
    %=e^{\langle w_f(\cdot,t,\theta),\mu\rangle},
    %\quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
%\end{equation}
    %where $w_f(x,t,\theta)$ satisfies the equation
\begin{align}\label{charequation}
    w_f(x,t,\theta)-\int_0^t T_{t-s} \psi \big(-w_f(\cdot,s,\theta)\big)(x)ds
    =i\theta T_tf(x),
    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
\end{align}
and
\begin{align}
\label{eq:chareq2}
    %w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x),
    w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-w_f(\cdot,s,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
\end{align}
%new added
%end new added
%begin comments
    {\bf Zhenyao: There are notation inconsistency in the Appendix and other suctions. Mainly on the branching mechanism: In the appendix, we use
\[
    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
\]
    But in other subsections we use
\[
    \psi(z) = - \alpha z + z^{1+\beta}.
\]
    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.

@@

For each $p\in \mathbb{Z}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
 We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0\leq\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $g \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(g)b(1+\beta)$, then as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa(g)b)t}\langle g, X_t\rangle \rightarrow\sum_{|p|=\kappa(g)}\langle g, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     for any $0\leq\gamma<\beta$.

     Moreover, if $g$ is twice differentiable and its twice derivative $D^2 g$ satisfies $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure.
 \end{thm}
For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{rem}
    If $\kappa(g)=0$, $\langle g, \phi_{\kappa(g)}\rangle_{\varphi}$ reduces to $\langle g,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle g, X_t\rangle \rightarrow \langle g, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0\leq\gamma<\beta$.

    Moreover, if $g$ is twice differentiable and $|D^2 g| \in \mathcal{P}$, then the convergence is almost sure.
 \end{rem}

\subsubsection{Critical Branching Rate}
For $g\in \mathcal{P}$, define
$$\tilde{m}[g]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
{\color{red}where}
$$\phi(x)=\sum_{|p|=\kappa(g)}\langle g,\phi_p\rangle\phi_p(x).$$
See Lemma \ref{lemma210} for more details about $\tilde{m}[g]$.
\begin{thm}\label{Theorem12}
Let $g\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle g,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[g]).$$
\end{thm}

@@

For $g\in \mathcal{P}$, define
$$m[g]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}g)^{1+\beta}(x)~ds~\varphi(x)~dx$$
In Lemma \ref{lemma211}, we will prove that $|m[g]|<\infty$.
\begin{thm}\label{Theorem13}
    If $g\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(g)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle g,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with characteristic function given by
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[g]).$$
\end{thm}

\section{Preliminaries}
In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in [0,\beta)$. 
%For notational convenience, we always fix $g\in \mathcal{P}$ in the following sections, correspondingly, there exists $R\in\mathcal{P}$ such that 
    In this section, we fix a $g\in \mathcal{P}$. 
    According to \eqref{eq:semigroupineq}, there exists an $R_0\in\mathcal{P}$ such that 
\begin{align}
     %|T_tg|\leq T_t|g|\leq e^{-\kappa(g)bt}R.
     |T_tg|(x)
     \leq e^{-\kappa(g)bt}R_0(x),
     \quad t\geq 0,x\in E.
\end{align}
%new added
Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R \in \mathcal P$ such that
\begin{align}
\label{eq:gcontrol}
    T_s|T_t g|(x) 
    \leq e^{-\kappa(g)bt} R(x), 
    \quad t\geq 0,s\geq 0,x\in E.
\end{align}
%end new added

Consider an incremental decomposition of $\langle g,X_t \rangle$. 
    %Denote by $\{\mathcal{F}_t:t\geq 0\}$ the filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$. 
    For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$. 
    %For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$. 
    For each $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$. 
    %For each $t-k\geq 1$, according to \eqref{eq:meanformula}, write
    For each $k \in \mathbb N$ and $t\geq k+1$, according to \eqref{eq:meanformula}, write
\begin{align*}
    M_k^t[g]:&=\langle g_k, X_{t-k}\rangle-\mathbb{P}_{\mu}(\langle g_k,X_{t-k}\rangle|\mathcal{F}_{t-k-1})\\
    &=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle\\
    &=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle.
\end{align*}
    %If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration. 
    For each $t\geq 0$, let $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration. 
    From now on, we assume $t$ is a positive integer, for simplicity. Thus
\begin{equation}\label{decomposition}
    \langle g,X_t\rangle
    =\sum_{k=0}^{t}M_k^t[g]
%new added
    , \quad t \in \mathbb N.
%end new added
\end{equation}

{\bf Jianjie: We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t \rfloor,t]$, which can be handled with the same techniques.
}
\subsection{Approximate expansion of characteristic function}

In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $w_{g_k}(x,s,\theta)$.
\begin{lem}\label{lemma1}
%For any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
    Let $R \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
%$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
\begin{equation}
    e^{-\alpha s}|w_{g_k}(x,s,\theta)|
    \leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), 
    \quad k\in \mathbb N, x\in \mathbb R^d, \theta \in \mathbb R, s\geq 0.
\end{equation}
\end{lem}
%comment
    {\bf Zhenyao: The statement of the above Lemma is changed. I think the old version is not correct. I'm not sure how this influence the rest of the paper.

    Also, there are some paragraphs below I deleted which are duplicated with the appendix.}
%end comment
%delete
    %Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$. Let $\mathbb{D}$ be the collection of $\mathcal{M}(\mathbb{R}^d)$-valued right continuous functions $t\rightarrow \omega_t$ on $(0,\infty)$ having zero as a trap. Denote by $\{\omega_t, t\geq0\}$ the coordinate process of $\mathbb{D}$ and $(\mathcal{C},\mathcal{C}_t)$ the natural $\sigma$-algebras on $\mathbb{D}$ generated by the coordinate process.

@@

From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-w_{g_k})\geq 0$.

@@

   &|w_{g_k}(x,s,\theta)-\tilde{w}_{g_k}(x,s,\theta)|
   \\&\leq \int_0^s T_{s-v}^{\alpha}\left(|(-w_{g_k}(\cdot,v,\theta))^{1+\beta}-(-i\theta T_v^{\alpha}g_k)^{1+\beta}|\right)(x)~dv
   \\&\leq C_0\int_0^s T_{s-v}^{\alpha}\left( |w_{g_k}(\cdot,v,\theta)-i\theta T_v^{\alpha}g_{k}|\left(|w_{g_k}(\cdot,v,\theta)|^{\beta}+|i\theta T_v^{\alpha}g_k|^{\beta}\right)\right)(x)~dv.

@@

    |w_{g_{k}}(x,v,\theta)|

>>>>

    = e^{-\langle u_f(t,\cdot), \mu \rangle},

@@

where $(t,x) \mapsto u_f(t,x)$ is the unique locally bounded positive solution to the equation

@@

     u_f(t,x) + \Pi_x \Big[ \int_0^t\psi\big(u_f(t-s, \xi_s)\big)~ds\Big]

@@

    The existence of such superprocesses is well known, see \cite{EB} for instance.
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
    The fact $\psi(\infty)=\infty$  and $\int^{\infty}\frac{1}{\psi(z)}~dz<\infty$ implies that the probability of extinguish event $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$ is contained in $(0,1)$, which means that our superprocess is non-persistent.
    In fact,
\begin{equation}
    \mathbb{P}_{\mu}(D)= \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$. See \cite[Theorem 12.5 \& Theorem 12.7]{Kyprianou2014Fluctuations} for a example.
%comment
   % {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq %0,~\text{s.t.}~\|X_t\|=0\}$. Because we want to emphsis that our superprocess is non-presistent.)}
%end comment
%comment
    {\bf (Jianjie: I rewrite this part to emphsis that our superprocess is non-presistent.)}
%end comment
    Define the \emph{Fenyman-Kac semigroup} by
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    := \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.

@@

    %In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
    In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is easy to see that $\mathcal{P} \subset L^2(\varphi)$.
    %According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R_0 \in \mathcal{P}$ such that,
\begin{equation}
\label{eq:semigroupineq}
    |T_tf(x)|
    \leq e^{-\kappa(f)bt} R_0(x),
    \quad t\geq 0, x\in \mathbb R^d.
\end{equation}

@@

    Let $X$ be the super OU-process discussed in the previous subsections.
    Its branching mechanism $\psi$ can be extended in the following way: $\psi(z) := -\alpha z + z^{1+\beta}$ for $z\in \mathbb C_+$.
    Then according to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
Write $\psi_0(z) = \psi(z) + \alpha z$ and $\psi'_0(z) = \psi'(z) + \alpha$.
%end new added
    %For any $f \in \mathcal{P}$, replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
%\begin{equation}\label{characteristic}
    %\mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
%\end{equation}
%where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
%\begin{equation}\label{charequation}
    %w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
%\end{equation}
    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $v_f(t,x,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta \langle f, X_t\rangle}]$ the characteristic exponent of $\{\langle f,X_t \rangle; \mathbb P_{\delta_x}\}$
    (For percise definition, see the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $- v_f(t,x,\theta)$ taks values in $\mathbb C_+$.
    Furthermore, we know from Proposition \ref{sec: definition of characteristic exponent} that
%delete
%\begin{equation}\label{characteristic}
    %\mathbb{P}_{\mu}[e^{i\theta X_t(f)}]
    %=e^{\langle w_f(\cdot,t,\theta),\mu\rangle},
    %\quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
%\end{equation}
    %where $w_f(x,t,\theta)$ satisfies the equation
\begin{align}\label{charequation}
    v_f(t,x,\theta)-\int_0^t T_{t-s} \psi \big(-v_f(s,\cdot,\theta)\big)(x)ds
    =i\theta T_tf(x),
    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
\end{align}
and
\begin{align}
\label{eq:chareq2}
    %w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x),
    v_f(t,x,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-v_f(s,\cdot,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
\end{align}
%new added
%end new added
%begin comments
    {\bf Zhenyao: There are notation inconsistency in the Appendix and other suctions. Mainly on the branching mechanism: In the appendix, we use
\[
    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
\]
    But in other subsections we use
\[
    \psi(z) = - \alpha z + z^{1+\beta}.
\]
    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.

@@

For each $p\in \mathbb{Z}_+^d$, we define
$$H_t^p:= e^{-(\alpha-|p|b)t}\langle\phi_p,X_t\rangle,\quad t\geq 0.$$
 We will prove (see Lemma \ref{lemma26}) that, if $\alpha\beta>|p|b(1+\beta)$, $H_t^p$ is a $\mathbb{P}_{\mu}$-martingale bounded in $L^{1+\gamma}(\mathbb{P}_{\mu})$ for any $0<\gamma<\beta$, thus the limit $H^p_{\infty}:=\lim_{t\rightarrow \infty}H_t^p$ exists $\mathbb{P}_{\mu}$-as and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{thm}\label{Theorem11}
     If $f \in \mathcal{P}$ satisfies $\alpha\beta>\kappa(f)b(1+\beta)$, then as $t\rightarrow \infty$,
     $$e^{-(\alpha-\kappa(f)b)t}\langle f, X_t\rangle \rightarrow\sum_{|p|=\kappa(f)}\langle f, \phi_p\rangle_{\varphi} H_{\infty}^p \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
     for any $0<\gamma<\beta$.

     Moreover, if $f$ is twice differentiable and its twice derivative $D^2 f$ satisfies $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
 \end{thm}
For any $t>0$, let $W_t:=e^{-\alpha t}\|X_t\|$, then $W_t$ is equal to $H_t^0$ and is a non-negative martingale with limit $W_{\infty}:=\lim_{t\rightarrow\infty}W_t$,  $\mathbb{P}_{\mu}$-a.s. and in $L^{1+\gamma}(\mathbb{P}_{\mu})$.
 \begin{rem}
    If $\kappa(f)=0$, $\langle f, \phi_{\kappa(f)}\rangle_{\varphi}$ reduces to $\langle f,\varphi\rangle$. Hence by Theorem \ref{Theorem11}, we get, as $t\rightarrow \infty$
     $$e^{-\alpha t}\langle f, X_t\rangle \rightarrow \langle f, \varphi\rangle W_{\infty} \quad in~ L^{1+\gamma}(\mathbb{P}_{\mu})$$
    for any $0<\gamma<\beta$.

    Moreover, if $f$ is twice differentiable and $|D^2 f| \in \mathcal{P}$, then the convergence is almost sure.
 \end{rem}

\subsubsection{Critical Branching Rate}
For $f\in \mathcal{P}$, define
$$\tilde{m}[f]:= \langle(-i\phi)^{1+\beta},\varphi\rangle$$
where
$$\phi(x)=\sum_{|p|=\kappa(f)}\langle f,\phi_p\rangle\phi_p(x).$$
See Lemma \ref{lemma210} for more details about $\tilde{m}[f]$.
\begin{thm}\label{Theorem12}
Let $f\in\mathcal{P}$, assume that  $\alpha\beta=\kappa(f)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
$$\frac{\langle f,X_t\rangle}{\left(t\|X_t\|\right)^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_1, \quad t\rightarrow \infty,$$
where $\eta_1$ is a $(1+\beta)$-stable random variable with characteristic function given by
$$\mathbb{E} [e^{i\theta \eta_1}]=\exp(\theta^{1+\beta}\tilde{m}[f]).$$
\end{thm}

@@

For $f\in \mathcal{P}$, define
$$m[f]:=\int_{\mathbb{R}^d}\int_0^{\infty} e^{-\alpha s}(-iT_{s}^{\alpha}f)^{1+\beta}(x)~ds~\varphi(x)~dx$$
In Lemma \ref{lemma211}, we will prove that $|m[f]|<\infty$.
\begin{thm}\label{Theorem13}
    If $f\in\mathcal{P}$ satisfies  $\alpha\beta<\kappa(f)b(1+\beta)$, then, under $\mathbb{P}_{\mu}(\cdot|D^c)$, it holds that
    $$\frac{\langle f,X_t\rangle}{\|X_t\|^{\frac{1}{1+\beta}}}\xrightarrow{d} \eta_2, \quad t\rightarrow \infty,$$
    where $\eta_2$ is a $(1+\beta)$-stable random variable with characteristic function given by
    $$\mathbb{E} [e^{i\theta \eta_2}]=\exp(\theta^{1+\beta}m[f]).$$
\end{thm}

\section{Preliminaries}
In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in (0,\beta)$.
%For notational convenience, we always fix $g\in \mathcal{P}$ in the following sections, correspondingly, there exists $R\in\mathcal{P}$ such that
    In this section, we assume a function $g$ satisfying that there exists $C_h, \kappa>0$ and $R^g_0\in \mathcal{P}$
    such that
\begin{align}
\label{eq:gcontrol1}
     |T_tg|(x)
     \leq C_g e^{-\kappa bt}R^g_0(x),
     \quad t\geq 0,x\in \mathbb{R}^d.
\end{align}
%new added
Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R^g \in \mathcal P$ such that
\begin{align}
\label{eq:gcontrol}
    T_s|T_t g|(x)
    \leq C_g e^{-\kappa bt} R^g(x),
    \quad t\geq 0,s\geq 0,x\in \mathbb{R}^d.
\end{align}
%end new added

Consider an incremental decomposition of $\langle g,X_t \rangle$.
    %Denote by $\{\mathcal{F}_t:t\geq 0\}$ the filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$.
    For each $t\geq 0$, denote by $\{\mathcal{F}_t:t\geq 0\}$ the natrual filtration of $X$, that is $\mathcal{F}_t=\sigma(X_s:s\in [0,t])$.
    %For $k \in \mathbb{N}$, let $g_k=T^{\alpha}_k g$.
    For each $f\in\mathcal{P}$ and $k \in \mathbb{N}$, let $f_k=T^{\alpha}_k f$.
    %For each $t-k\geq 1$, according to \eqref{eq:meanformula}, write
    %For each $k \in \mathbb N$ and $t\geq k+1$, 
    According to \eqref{eq:meanformula}, write
\begin{align*}
    M_k^t[g]:&=\langle g_k, X_{t-k}\rangle-\mathbb{P}_{\mu}(\langle g_k,X_{t-k}\rangle|\mathcal{F}_{t-k-1})\\
    &=\langle g_k, X_{t-k}\rangle-\langle T_1^{\alpha}g_{k},X_{t-k-1}\rangle\\
    &=\langle g_k, X_{t-k}\rangle-\langle g_{k+1},X_{t-k-1}\rangle, \quad t\geq k+1.
\end{align*}
    %If $k=t$, let $M_t^t[g]:=\langle g_t,\mu\rangle$, where $\mu $ is the initial configuration.
    What's more, we denote $M_{\lfloor t\rfloor}^t[g]:=\langle g_{\lfloor t \rfloor},X_{t-\lfloor t\rfloor}\rangle-\langle g_t, \mu\rangle$ and $M_t^t[g]:=\langle g_t,\mu\rangle$ under $\mathbb P_\mu$, where $\mu $ is the initial configuration. Thus
\begin{equation}\label{decomposition}
    \langle g,X_t\rangle-M_t^t[g]
    =\sum_{k=0}^{\lfloor t\rfloor}M_k^t[g]
%new added
    , \quad t \geq 0.
%end new added
\end{equation}

%{\bf Jianjie: We have to emphasize that, if $t\notin \mathbb{N}$, there will appear an additional term corresponding to the interval $[\lfloor t %\rfloor,t]$, which can be handled with the same techniques.
%}
\subsection{Approximate expansion of characteristic function}

In this subsection, we will estimate the characteristic function of $M_k^t[g]$ near $0$. First, we will prove the following inequality which controls $v_{g_k}(s,x,\theta)$.
\begin{lem}\label{lemma1}
%For any $k \in \mathbb{N}$, $x\in\mathbb{R}^d$ and $\theta\in \mathbb{R}$, we have
    Let $R^g \in \mathcal P$ be the control function in \eqref{eq:gcontrol}, then
%$$e^{-(\alpha-\kappa(g)b) s}|w_{g_k}(x,s,\theta)|\leq |\theta|e^{(\alpha-\kappa(g)b)k} R(x), \quad s\geq 0.$$
\begin{equation}
    e^{-\alpha s}|v_{g_k}(s,x,\theta)|
    \leq C_g|\theta|e^{(\alpha-\kappa b)k} R^g(x),
    \quad k\in \mathbb N, x\in \mathbb R^d, \theta \in \mathbb R, s\geq 0.
\end{equation}
\end{lem}
%comment
   % {\bf Zhenyao: The statement of the above Lemma is changed. I think the old version is not correct. I'm not sure how this influence the rest of the paper.

    % Also, there are some paragraphs below I deleted which are duplicated with the appendix.}
%end comment
%delete
    %Recall some result about the Kuznestov measures of $\{X_t, t\geq 0\}$. Let $\mathbb{D}$ be the collection of $\mathcal{M}(\mathbb{R}^d)$-valued right continuous functions $t\rightarrow \omega_t$ on $(0,\infty)$ having zero as a trap. Denote by $\{\omega_t, t\geq0\}$ the coordinate process of $\mathbb{D}$ and $(\mathcal{C},\mathcal{C}_t)$ the natural $\sigma$-algebras on $\mathbb{D}$ generated by the coordinate process.

@@

From \eqref{eq: -v has positive real part} we know that $\operatorname{Re}(-v_{g_k})\geq 0$.

@@

   &|v_{g_k}(s,x,\theta)-\tilde{v}_{g_k}(s,x,\theta)|
   \\&\leq \int_0^s T_{s-u}^{\alpha}\left(|(-v_{g_k}(u,\cdot,\theta))^{1+\beta}-(-i\theta T_u^{\alpha}g_k)^{1+\beta}|\right)(x)~du
   \\&\leq C_0\int_0^s T_{s-u}^{\alpha}\left( |v_{g_k}(u,\cdot,\theta)-i\theta T_u^{\alpha}g_{k}|\left(|v_{g_k}(u,\cdot,\theta)|^{\beta}+|i\theta T_u^{\alpha}g_k|^{\beta}\right)\right)(x)~du.

@@

    |v_{g_{k}}(u,x,\theta)|
    &\leq C_g|\theta|e^{(\alpha-\kappa b)k+\alpha}R^g(x),
